---
title: "textBits: Bits and Pieces of Code for Acquiring, Cleaning, and Working with Text"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
devtools::source_gist("c83e078bf8c81b035e32c3fc0cf04ee8", 
                      filename = 'render_toc.R')
```

This is a clearinghouse for bits and pieces of code pertaining to gathering, cleaning, and working with text. In many cases, the code here will have been put together to help a researcher with a specific problem; if I think it might be more broadly useful, I'll share it here. And some of these items are just bits that I think are kind of cool.

```{r toc, echo=FALSE} 
render_toc("README.Rmd")
```

## Prepping Data from Specific Sources
### Prepping News Articles from Nexis Uni (Folder: `nexisUniNews`)
The `processNexisNews` function reads PDFs of news articles downloaded from Nexis Uni into R, domes some parsing and cleaning, and stores as a dataframe. Source the [`nexisFunctions.R `](https://github.com/burrowsdt/textBits/blob/main/nexisUniNews/nexisFunctions.R) file and then run the function with the filepath to the folder with all of your articles as an argument (see below). See the [vignette](https://github.com/burrowsdt/textBits/blob/main/nexisUniNews/NexisUniNewsArticles.pdf) for a quick overview.
```{r message=FALSE, warning=FALSE, paged.print=FALSE}
source("nexisUniNews/nexisFunctions.R")
processNexisNews("nexisUniNews/data/")
```

